---
title: GGM compare
author: Donald R. Williams
date: September 09, 2020
output: html_document
---


# Simulation 1: error rate under null hypothesis
```{r, message=FALSE}
# packages
library(BGGM)
library(MASS)
library(dplyr)
library(knitr)
library(corpcor)
library(ggplot2)
library(cowplot)
library(igraph)
library(ggraph)
library(reshape)
library(ggridges)
library(qgraph)

# windows font
windowsFonts(Times = windowsFont("Times New Roman")) 
```

```{r, eval = FALSE}
# sample sizes
n1 <- c(250, 500, 1000)
n2 <- c(250, 500, 1000)

# number of variable
p <- 16

# simulation conditions
sim_cond <- rbind(cbind(n1, n2),  cbind(n1, n2 * .5))

# correlation to partial correlation
pcors <- cor2pcor(ptsd_cor4)

# threshold values less than 0.05
pcors <- ifelse(abs(pcors) < 0.05, 0, pcors)

# "true" covariance matrix
cov_mat <- pcor2cor(pcors)


map_func <- function(n1, n2){
# groups
Y_g1 <- MASS::mvrnorm(n1, rep(0, 16), Sigma = cov_mat)
Y_g2 <- MASS::mvrnorm(n2, rep(0, 16), Sigma = cov_mat)

# fit model
fit <- ggm_compare_ppc(Y_g1, Y_g2, 
                       type = "global", 
                       iter = 1000)

# yes: equal sample sizeshey
if(n1 == n2){
  results <- data.frame(p = fit$pvalue, n = n1,  type = "equal")
}
# not: equal sample sizes
else{
  results <- data.frame(p = fit$pvalue, n = n1,  type = "unequal")
  }
# return
return(results)
}

# simulation
simulation <- pbapply::pbreplicate(1000,
                          do.call(rbind.data.frame, mapply(map_func,
                                                           n1 = sim_cond[,1],
                                                           n2 = sim_cond[,2],
                                                           SIMPLIFY = F)), simplify = F)
# results_sim1 <- do.call(rbind.data.frame, simulation)
# save(results_sim1, file = "results_sim1.Rdata")
# write.csv(results_sim1, file = "results_sim1.csv")
```

```{r}
load("results_sim1.Rdata")
results_sim1 %>% 
    group_by(n, type) %>% 
     summarise(Error_rate = mean(p < 0.05), 
               MCE = (mean(p < 0.05) * (1 - mean(p < 0.05)))/ sqrt(n()) ) %>%
  kable()
```


# Example plot: predictive distribution
```{r, message=F, eval = F}
pcors <- cor2pcor(ptsd_cor4)

# threshold values less than 0.05
pcors <- ifelse(abs(pcors) < 0.05, 0, pcors)

# "true" covariance matrix
cov_mat <- pcor2cor(pcors)

# n = 250
n1 <- 250
n2 <- 250
Y_g1 <- MASS::mvrnorm(n1, rep(0, 16), cov_mat)
Y_g2 <- MASS::mvrnorm(n2, rep(0, 16), cov_mat)

# fit 250
fit_250 <- ggm_compare_ppc(Y_g1, Y_g2, type = "global", iter = 10000)


# n = 500
n1 <- 500
n2 <- 500
Y_g1 <- MASS::mvrnorm(n1, rep(0, 16), cov_mat)
Y_g2 <- MASS::mvrnorm(n2, rep(0, 16), cov_mat)

# fit 500
fit_500 <-   ggm_compare_ppc(Y_g1, Y_g2, type = "global", iter = 10000)


# n = 1000
n1 <- 1000
n2 <- 1000
Y_g1 <- MASS::mvrnorm(n1, rep(0, 16), cov_mat)
Y_g2 <- MASS::mvrnorm(n2, rep(0, 16), cov_mat)

# fit 1000
fit_1000 <- ggm_compare_ppc(Y_g1, Y_g2, 
                            type = "global", 
                            iter = 10000)


# predictive JSD (symmetric KL)
ppc <- c(fit_250$predictive_risk, 
         fit_500$predictive_risk, 
         fit_1000$predictive_risk)

# data predictive JSD
dat_ppc <- data.frame(ppc = unlist(ppc),
                      contrast = rep(c("250", "500", "1000"), each = 10000))

# factor levels
dat_ppc$contrast <- factor(dat_ppc$contrast, 
                           labels = c("250", "500", "1000"),  
                           levels = c("250", "500", "1000")) 

# observed JSD 
obs <- c(fit_250$obs_jsd[[1]], 
         fit_500$obs_jsd[[1]], 
         fit_1000$obs_jsd[[1]])
dat_obs <- data.frame(ppc = obs, contrast =  c("250", "500", "1000"))

# factor levels
dat_obs$contrast <- factor(dat_obs$contrast, 
                           labels = c("250", "500", "1000"),  
                           levels = c("250", "500", "1000")) 



critical = 0.05
col_noncritical = "#84e184A0" 
col_critical = "red"
point_size = 3

# plot 1A
plot_1A <- ggplot(dat_ppc, aes(x = ppc,
                           y = as.factor(contrast),
                           fill = factor(..quantile..))) +
  stat_density_ridges(geom = "density_ridges_gradient",
                      calc_ecdf = TRUE, 
                      alpha = 0.5,
                      quantiles = c(0.025, 1 - (critical))) +
  scale_fill_manual( values = c(col_noncritical, 
                                col_noncritical, 
                                col_critical)) +
  theme(legend.position = "none") +
  scale_y_discrete(expand = c(0.05, 0)) +
  theme_bw(base_family = "Times", 
           base_size = 14) +
  theme(legend.position = "none", 
        panel.grid = element_blank()) +
  geom_point(inherit.aes = F,
           data = dat_obs,
           aes(x = ppc,
               y = contrast),
           size = point_size) +
  ylab("Sample Size") +
  xlab("Predictive Distribution") 

#save(plot_1A, file = "plot_1A.Rdata" )
```

# Simulation 2: Comparison to NCT
```{r, eval = FALSE}
# total n
n_total <- c(500, 1000, 2000)

# sample sizes
n1 <-  c(c(250, 500, 1000), n_total * .6,  n_total -  n_total * .6)
n2  <- c(c(250, 500, 1000), n_total -  n_total * .6, n_total * .6)

# df condition
df_cond <- rbind(cbind.data.frame(n1, n2, cut = 0.075, type = "cut"),
                 cbind.data.frame(n1, n2, cut = 0, type = "reduce"), 
                 cbind.data.frame(n1, n2, cut = 0.075, type = "both"))

for(j in 1:nrow(df_cond)){
  for(i in 1:100){
    
    print(paste("condition", j, "iteration", i))
    
    # simulation condition
    df_sim <- df_cond[j,]
    
    # baseline partial correlation matrix
    pcor4 <- corpcor::cor2pcor(as.matrix(BGGM::ptsd_cor4))
    pcor4 <- ifelse(abs(pcor4) < 0.05, 0, pcor4) 
    
    # cut values less than 0.075
    if(df_sim$type == "cut"){
      pcor4_new <- ifelse(abs(pcor4) < df_sim$cut, 0, pcor4)
    }
    # reduce largest by 75 %
    if(df_sim$type == "reduce"){
      pcor4_new <- pcor4
      pcor4_new[1,3] <-  pcor4[1,3] *.75 
      pcor4_new[3,1] <-  pcor4[1,3] *.75
      
    }
   # reduce and cut
    if(df_sim$type == "both"){
      pcor4_new <- ifelse(abs(pcor4) < df_sim$cut, 0, pcor4)
      pcor4_new[1,3] <-  pcor4[1,3] *.75 
      pcor4_new[3,1] <-  pcor4[1,3] *.75
    }
    
    # baseline correlation matrix
    cor4 <- corpcor::pcor2cor(pcor4)
    
    # altered correlation matrix
    cor4_new <- corpcor::pcor2cor(pcor4_new)
    
    # generate data
    Y_g1 <- MASS::mvrnorm(df_sim$n1, mu = rep(0, 16), Sigma =  cor4)
    Y_g2 <- MASS::mvrnorm(df_sim$n2, mu = rep(0, 16), Sigma =  cor4_new)
    
    # predictive method 
    ppc <- ggm_compare_ppc(Y_g1, Y_g2, 
                           type = "global", 
                           iter = 500, 
                           cores = 2)
    
    # ppc p-value
    ppc_pvalue <-  ifelse(ppc$pvalue <=  0.05, 1, 0)
   
    # NCT method
    suppressMessages({nct <- NetworkComparisonTest::NCT(Y_g1, 
                                                        Y_g2, 
                                                        it = 500, 
                                                        gamma = 0.5, 
                                                        progressbar = F)})
    
    # nct p-value
    nct_glstr_pvalue   <- ifelse(nct$glstrinv.pval <= 0.05, 1, 0)
    nct_nwinv_pvalue   <- ifelse(nct$nwinv.pval <= 0.05, 1, 0)
    
    if(df_sim$n1 == df_sim$n2){
      which_cut <- "equal" 
      }
    if(df_sim$n1 < df_sim$n2){
      which_cut <- "large_cut" 
    }
    if(df_sim$n1 > df_sim$n2){
      which_cut <- "small_cut" 
    }
    # returned results for "i" iterations
    res_i[[i]] <- data.frame(method = c("ppc", "nct_glstr", "nct_nwinv"), 
                            n1 = df_sim$n1, n2 = df_sim$n2, 
                            total_n = df_sim$n1 + df_sim$n2,
                            cutoff = df_sim$cut, 
                            which_cut = which_cut,
                            type = df_sim$type,
                            score = c(ppc_pvalue, 
                                      nct_glstr_pvalue,  
                                      nct_nwinv_pvalue))
    }
  
  # returned results for "j" conditions
  res_j[[j]] <- do.call(rbind.data.frame, res_i)
  
}

#results_sim2 <- res_j
#save(results_sim2, file = "results_sim2.Rdata")
```

# Simulation 2: plot 1B
```{r}
load("results_sim2.Rdata")

# combine results
df_results <- do.call(rbind.data.frame, results_sim2) 

# rename for facets
df_results$type <- factor(df_results$type, 
                          levels = c("cut", "reduce", "both"), 
                          labels = c("Cut", "Reduce", "Both"))

df_results$which_cut <- factor(df_results$which_cut, 
                               levels = c("equal", "small_cut", "large_cut"),
                               labels =  c("Equal", 
                                           "Smallest Group Changed", 
                                           "Largest Group Chanaged"))

# plot 1B
plot_1B <- df_results %>%
group_by(method, total_n, which_cut, type) %>% 
  summarise(mu_score = mean(score)) %>% 
  ggplot(aes(x = as.factor(total_n), 
             y = mu_score, 
             group = method, 
             color = method)) +
  facet_grid(type ~  which_cut) +
  theme_bw(base_family = "Times", 
           base_size = 14) +
  geom_line(size = 1.5) +
  theme(legend.position = "top", 
        strip.background = element_rect(fill = "grey94"),
        panel.spacing = unit(.5, "lines"),
        panel.grid.minor.y = element_blank(),
        legend.background = element_rect(color = "black"), 
        panel.grid = element_line(color = "grey97")) +
  ylab("Power") +
  xlab("Sample Size") +
  scale_color_manual(values = c("#009E73", "#D55E00", "#0072B2"), 
                     name = "Method", 
                     breaks = c("ppc", "nct_glstr", "nct_nwinv"), 
                     labels = c("Predictive", "NCT (a)", "NCT (b)") )

#save(plot_1B, file = "plot_1B.Rdata" )
```


# Illustrative Example: predictive
```{r, eval = FALSE}
Y_g1 <- MASS::mvrnorm(n = 526, rep(0, 16), Sigma = BGGM::ptsd_cor1, empirical = T)
Y_g2 <- MASS::mvrnorm(n = 365, rep(0, 16), Sigma = BGGM::ptsd_cor2, empirical = T)
Y_g3 <- MASS::mvrnorm(n = 926, rep(0, 16), Sigma = BGGM::ptsd_cor3, empirical = T)
Y_g4 <- MASS::mvrnorm(n = 956, rep(0, 16), Sigma = BGGM::ptsd_cor4, empirical = T)

fit <- ggm_compare_ppc(Y_g1, Y_g2, 
                       Y_g3, Y_g4, 
                       type = "global", 
                       iter = 5000, 
                       cores = 4)

# save(fit, file = "fit.Rdata")
```


# Plot 1C
```{r,message=F, warning=F, eval=FALSE}
fit_node <- ggm_compare_ppc(Y_g1, Y_g2, Y_g3, Y_g4, type = "nodewise", iter = 5000, cores = 4)

load("fit.Rdata")

plot_1C <- plot(fit, log = TRUE, point_size = 3) + 
  theme_bw(base_family = "Times", 
           base_size = 14) +
  theme(legend.position = "none", 
        panel.grid = element_blank()) +
  scale_y_discrete(expand = c(0.05, 0)) +
  ylab("Sample Size") +
  xlab("Predictive Distribution") 

# save(plot_1C, file = "plot_1C.Rdata" )
```

# Nodewise results
```{r}
load("fit_node.Rdata")

for(i in 1:6){
critical <- apply(log(do.call(rbind, fit_node$predictive_risk[[i]])), 2, quantile,  0.95)
obs <- log(as.numeric(fit_node$obs_jsd[[i]]))
p <- as.numeric(fit_node$pvalue[[i]])
node <- 1:16
print(kable(data.frame(node = node, 
                       critical = critical, 
                       observed = obs, 
                       p_value = p),
            digits = 2, 
            caption = fit_node$names[[i]]))
}
```



# Simulation 3: Hyperparameter Selection
```{r, eval = FALSE}
cond <- expand.grid(d = c(10, 20, 40),
                    n = c(100, 200, 400),
                    groups = c(2,3,4),
                    reduce = c(0, 0.25, 0.75, 1))


res_i <- list()
res_j <- list()

for(j in 1:nrow(cond)){
  for(i in 1:100){

    print( paste("condition", j, "iteration", i) )
    sim_cond <- cond[j,]

    if(sim_cond$groups == 2){
      samp_reduce <- 0.4639371 * sim_cond$reduce

      mat_dif <- corpcor::cor2pcor(BGGM::ptsd_cor4)

      mat_dif[1,3] <- samp_reduce
      mat_dif[3,1] <- samp_reduce

      X1 <- MASS::mvrnorm(n = sim_cond$n,
                          rep(0, 16),
                          Sigma = corpcor::pcor2cor(mat_dif),
                          empirical = F)

      X2 <- MASS::mvrnorm(n = sim_cond$n,
                          rep(0, 16),
                          Sigma = BGGM::ptsd_cor4,
                          empirical = F)

      fit <- ggm_compare_bf(X1, X2,
                     prior_sd = 1/sqrt(sim_cond$d),
                     iter = 5000,
                     cores = 2)

      BF_10 <- 1 / fit$BF_01[1,3]
      prob_10 <- BF_10 / (BF_10 + 1)


     res <-  data.frame(n = sim_cond$n,
                         delta = sim_cond$d,
                         groups = sim_cond$groups,
                         reduce = sim_cond$reduce,
                         prob_10 = prob_10,
                         diff = samp_reduce -  0.4639371 )

    }


    if(sim_cond$groups == 3){
      samp_reduce <- 0.4639371 * sim_cond$reduce

      mat_dif <- corpcor::cor2pcor(BGGM::ptsd_cor4)

      mat_dif[1,3] <- samp_reduce
      mat_dif[3,1] <- samp_reduce

      X1 <- MASS::mvrnorm(n = sim_cond$n,
                          rep(0, 16),
                          Sigma = corpcor::pcor2cor(mat_dif),
                          empirical = F)

      X2 <- MASS::mvrnorm(n = sim_cond$n,
                          rep(0, 16),
                          Sigma = BGGM::ptsd_cor4,
                          empirical = F)

      X3 <- MASS::mvrnorm(n = sim_cond$n,
                          rep(0, 16),
                          Sigma = BGGM::ptsd_cor4,
                          empirical = F)

      fit <- ggm_compare_bf(X1, X2, X3,
                            prior_sd = 1/sqrt(sim_cond$d),
                            iter = 5000,
                            cores = 2)

      BF_10 <- 1 / fit$BF_01[1,3]
      prob_10 <- BF_10 / (BF_10 + 1)


      res <-  data.frame(n = sim_cond$n,
                         delta = sim_cond$d,
                         groups = sim_cond$groups,
                         reduce = sim_cond$reduce,
                         prob_10 = prob_10,
                         diff = samp_reduce -  0.4639371)
      }


    if(sim_cond$groups == 4){

      samp_reduce <- 0.4639371 * sim_cond$reduce

      mat_dif <- corpcor::cor2pcor(BGGM::ptsd_cor4)

      mat_dif[1,3] <- samp_reduce
      mat_dif[3,1] <- samp_reduce

      X1 <- MASS::mvrnorm(n = sim_cond$n,
                          rep(0, 16),
                          Sigma = corpcor::pcor2cor(mat_dif),
                          empirical = F)

      X2 <- MASS::mvrnorm(n = sim_cond$n,
                          rep(0, 16),
                          Sigma = BGGM::ptsd_cor4,
                          empirical = F)

      X3 <- MASS::mvrnorm(n = sim_cond$n,
                          rep(0, 16),
                          Sigma = BGGM::ptsd_cor4,
                          empirical = F)

      X4 <- MASS::mvrnorm(n = sim_cond$n,
                          rep(0, 16),
                          Sigma = BGGM::ptsd_cor4,
                          empirical = F)

      fit <- ggm_compare_bf(X1, X2, X3, X4,
                            prior_sd = 1/sqrt(sim_cond$d),
                            iter = 5000,
                            cores = 2)

      BF_10 <- 1 / fit$BF_01[1,3]
      prob_10 <- BF_10 / (BF_10 + 1)


      res <-  data.frame(n = sim_cond$n,
                         delta = sim_cond$d,
                         groups = sim_cond$groups,
                         reduce = sim_cond$reduce,
                         prob_10 = prob_10,
                         diff = samp_reduce -  0.4639371)
    }
    res_i[[i]] <- res
    }
  res_j[[j]] <- do.call(rbind.data.frame, res_i)
  save(res_j, file = "res_j.Rdata")
}

# results_sim3 <- res_j
# save(results_sim3, file = "results_sim3.Rdata")
```

# Simulation 3: Plot 1A
```{r}
load("results_sim3.Rdata")

res_df_3 <- do.call(rbind.data.frame, results_sim3)

res_df_3_summ <- res_df_3 %>%
  group_by(n, delta, groups, diff) %>%
  summarise(mu  = mean(prob_10),
            low = HDInterval::hdi(prob_10, 0.90)[1],
            up = HDInterval::hdi(prob_10, 0.90)[2],
            sd = sd(prob_10))

res_df_3_summ$groups <- factor(res_df_3_summ$groups,
                               levels = c("2", "3", "4"),
                               labels = c("2 Groups", 
                                          "3 Groups", 
                                          "4 Groups"))

res_df_3_summ$n <- factor(res_df_3_summ$n,
                          levels = c("100", 
                                     "200", 
                                     "400"),
                          labels = c("n = 100", 
                                     "n = 200", 
                                     "n = 400"))

plot_3A <- res_df_3_summ  %>% filter(n != "n = 400") %>%
  ggplot(aes(x = as.factor(rev(diff)),
             fill = as.factor(delta),
             y = mu)) +
  geom_errorbar(aes(ymax = up, ymin  = mu), 
                position = position_dodge(1), 
                width = 0, 
                size = 1) +
  geom_bar(stat = "identity", 
           position = position_dodge(1)) +
  geom_errorbar(aes(ymax = mu, ymin  = low),
                position = position_dodge(1),
                width = 0,
                size = 1,
                color = "white") +
  theme_bw() +
  facet_grid(n ~ groups) +
  scale_fill_manual(name = "Method", 
                    values = c( "#009E73", 
                                "#0072B2", 
                                "#CC79A7"),
                    breaks = c("10", "20", "30", "40"),
                    labels = c("  10", "  20", "  30", "  40")) +
  scale_linetype_manual(name = "Method", 
                        values = c("dotted", 
                                   "longdash", 
                                   "dotdash")) +
  theme_bw(base_family = "Times", base_size = 13) +
  theme(legend.position = "none", 
        strip.background = element_rect(fill = "grey93"),
        panel.grid.minor.y = element_blank(),
        legend.background = element_rect(color = "black"),
        panel.grid = element_line(color = "grey93")) +
  ylab("Posterior Probability (H_1)") +
  xlab("Percent Reduction") +
  scale_x_discrete( labels = c("0 %", "25 %", "75 %", "100 %"))

# save(plot_3A, file = "plot_3A.Rdata")
```

# Simulation 4: Error Rates
```{r, eval=FALSE}
# partial correlations
pcors <- corpcor::cor2pcor(BGGM::ptsd_cor4)

# set less than 0.1 to zero
pcors <- ifelse(abs(pcors) < 0.1, 0, pcors)

# switch labels
null_mat <- ifelse(pcors == 0, 1, 0)


# mle fisher z
mle_fisher <- function(x, y){
  x <- scale(x, scale = F)
  y <- scale(y, scale = F)
  n <- nrow(x)
  p <- ncol(x)
  k  <- p - 1
  mat <- matrix(0, p, p)
  se_diff <- sqrt( (1 / (n - k - 3)) + (1 / (n - k - 3)) )
  x_pcs  <- cov2cor(solve(nrow(x)^-1 *   t(x) %*% x)) * -1
  y_pcs  <- cov2cor(solve(nrow(y)^-1 *   t(y) %*% y)) * -1
  pcs_diff <- BGGM:::fisher_z(x_pcs[upper.tri(x_pcs)]) - BGGM:::fisher_z(y_pcs[upper.tri(y_pcs)])
  z_score <- abs(pcs_diff / se_diff)
  pvalues <- (1 - pnorm(z_score)) * 2
  mat[upper.tri(mat)] <- ifelse(pvalues < 0.01, 1, 0)
  mat
}

cond <- expand.grid(d = c(10, 20, 40),
                    n = c(100, 250, 500, 1000),
                    groups = c(2,3,4))


res_i  <- list()
res_j <- list()

for(j in 1:nrow(cond)){
  for(i in 1:100){
    print( paste("condition", j, "iteration", i) )
    sim_cond <- cond[j,]
    
    if(sim_cond$groups == 2){
      
      X1 <- MASS::mvrnorm(n = sim_cond$n, rep(0, 16), 
                          Sigma = corpcor::pcor2cor(pcors), 
                          empirical = F)
      
      X2 <- MASS::mvrnorm(n = sim_cond$n, rep(0, 16), 
                          Sigma = diag(16), empirical = F)
      
      fit <- ggm_compare_bf(X1, X2, 
                            prior_sd = 1/sqrt(sim_cond$d), 
                            iter = 5000, 
                            cores = 4)
        
      bf_select_10 <- ifelse(1 / fit$BF_01 > 3, 1, 0)
      bf_select_01 <- ifelse(fit$BF_01 > 3, 1, 0)
      
      res_10 <-  BGGM:::performance(True = bf_select_10, 
                                    Estimate = pcors)$results[1:2,2]
      
      res_01 <-  BGGM:::performance(True = bf_select_01, 
                                    Estimate = null_mat)$results[1:2,2]
      
      fit_mle <- mle_fisher(X1, X2)
      mle_10 <-   BGGM:::performance(True = fit_mle, 
                                     Estimate = pcors)$results[1:2,2]
      
      
      res <- data.frame(n = sim_cond$n,
                        delta= sim_cond$d,
                        groups = sim_cond$groups,
                        method = rep(c("BF_alt", "BF_null", "mle"), 2),
                        measure = rep( c("SPC", "SN"), each = 3 ),
                        score = as.numeric(c(res_10[1], res_01[1], mle_10[1],
                                             res_10[2], res_01[2], mle_10[2])))
      
    }
    
    
    if(sim_cond$groups == 3){
      
      X1 <- MASS::mvrnorm(n = sim_cond$n, 
                          rep(0, 16), 
                          Sigma = corpcor::pcor2cor(pcors), 
                          empirical = F)
      X2 <- MASS::mvrnorm(n = sim_cond$n, 
                          rep(0, 16), 
                          Sigma = diag(16), 
                          empirical = F)
      X3 <- MASS::mvrnorm(n = sim_cond$n, 
                          rep(0, 16), 
                          Sigma = diag(16), 
                          empirical = F)
      
      fit <- ggm_compare_bf(X1, X2, X3,
                            prior_sd = 1/sqrt(sim_cond$d), 
                            iter = 5000, 
                            cores = 4)
      
      
      bf_select_10 <- ifelse(1 / fit$BF_01 > 3, 1, 0)
      bf_select_01 <- ifelse(fit$BF_01 > 3, 1, 0)
      
      
      res_10 <-  BGGM:::performance(True =  bf_select_10, 
                                    Estimate = pcors)$results[1:2, 2]
      
      res_01 <-  BGGM:::performance(True = bf_select_01, 
                                     Estimate = null_mat)$results[1:2,2]
      
      
      
      res <- data.frame(n = sim_cond$n,
                        delta= sim_cond$d,
                        groups = sim_cond$groups,
                        method = rep(c("BF_alt", "BF_null"), 2),
                        measure = rep( c("SPC", "SN"), each = 2 ),
                        score = as.numeric(c(res_10[1], res_01[1],
                                             res_10[2], res_01[2])))
      
    }
    
    if(sim_cond$groups == 4){
      
      
      X1 <- MASS::mvrnorm(n = sim_cond$n, 
                          rep(0, 16), 
                          Sigma = corpcor::pcor2cor(pcors), 
                          empirical = F)
      
      X2 <- MASS::mvrnorm(n = sim_cond$n, 
                          rep(0, 16), 
                          Sigma = diag(16), 
                          empirical = F)
      
      X3 <- MASS::mvrnorm(n = sim_cond$n, 
                          rep(0, 16), 
                          Sigma = diag(16), 
                          empirical = F)
      
      X4 <- MASS::mvrnorm(n = sim_cond$n, 
                          rep(0, 16), 
                          Sigma = diag(16), 
                          empirical = F)
      
      fit <- ggm_compare_bf(X1, X2, X3, X4,
                            prior_sd = 1/sqrt(sim_cond$d), 
                            iter = 5000, 
                            cores = 4)
      
      
      bf_select_10 <- ifelse(1 / fit$BF_01 > 3, 1, 0)
      bf_select_01 <- ifelse(fit$BF_01 > 3, 1, 0)
      
      res_10 <-  BGGM:::performance(True =  bf_select_10, 
                                    Estimate = pcors)$results[1:2, 2]
      
      res_01 <-  BGGM:::performance(True = bf_select_01, 
                                    Estimate = null_mat)$results[1:2,2]
      
      
      
      res <- data.frame(n = sim_cond$n,
                        delta= sim_cond$d,
                        groups = sim_cond$groups,
                        method = rep(c("BF_alt", "BF_null"), 2),
                        measure = rep( c("SPC", "SN"), each = 2 ),
                        score = as.numeric(c(res_10[1], res_01[1],
                                             res_10[2], res_01[2])))
      }
    res_i[[i]] <- res
    }
  res_j[[j]] <- do.call(rbind.data.frame, res_i)
  save(res_j, file = "res_j.Rdata")
}

# results_sim4 <- res_j
# save(results_sim4, file = "results_sim4.Rdata")
```

# Simulation 4: Plot Legend
```{r}
load("results_sim4.Rdata")
res_df_4 <- do.call(rbind.data.frame, results_sim4)

res_df_4_summ <- res_df_4 %>%
  group_by(n, delta, groups, method, measure) %>%
  summarise(mu = mean(score), sd_score = sd(score),
            up = HDInterval::hdi(score)[2],
            low = HDInterval::hdi(score)[1] )

res_df_4_summ$measure <- factor(res_df_4_summ$measure, 
                                levels = c("SPC", "SN"), 
                                labels = c("SPC", "SN"))

res_df_4_summ$groups <- factor(res_df_4_summ$groups,
                               levels = c("2", "3", "4"),
                               labels = c("2 Groups", 
                                          "3 Groups", 
                                          "4 Groups"))

# dummy data for mle
mle_temp <-  res_df_4_summ %>% 
  filter(method == "mle", 
         delta == 10)

mle_temp$delta <- 100

res_df_4_summ <- res_df_4_summ %>% 
                 filter(method != "mle")

res_df_4_summ <- rbind(mle_temp, res_df_4_summ)


# legend
plt_leg <- res_df_4_summ %>%
  filter(method != "BF_null") %>%
  ggplot(aes(x = as.factor(n), 
             y = mu, 
             group = delta, 
             fill = as.factor(delta))) +
  geom_errorbar(aes(ymax = up, 
                    ymin  = mu + 0, 
                    group = as.factor(delta)),
                position = position_dodge(1), 
                width = 0, 
                size = 1) +
  geom_bar(stat = "identity", 
           position = position_dodge(1)) +
  geom_errorbar(aes(ymax = mu, 
                    ymin  = low),
                position = position_dodge(1),
                width = 0,
                size = 1,
                color = "white") +
  theme_bw() +
  facet_grid(measure ~ groups) +
  scale_fill_manual(name = "Method", values = c( "#009E73", 
                                                 "#0072B2", 
                                                 "#CC79A7", 
                                                 "#999999"),
                    breaks = c("10", "20", 
                               "30", "40", "100"),
                    labels = c(expression(~delta~" = 10"), 
                               expression(~delta~" = 20"), 
                               expression(~delta~" = 30"),   
                               expression(~delta~" = 40"),
                               " MLE")) +
  theme_bw(base_family = "Times", 
           base_size = 13) +
  theme(legend.position = "top", 
        strip.background = element_rect(fill = "grey93"),
        panel.grid.minor.y = element_blank(),
        legend.background = element_rect(color = "black"),
        panel.grid = element_line(color = "grey93")) +
  ylab("Score") +
  xlab("Sample Size")

# get legend
leg <- cowplot::get_legend(plt_leg)
```

Simulation 4: Plot 3B
```{r}
plot_3B <- res_df_4_summ %>%
  filter(method != "BF_null") %>%
  ggplot(aes(x = as.factor(n), y = mu, group = delta, fill = as.factor(delta))) +
  geom_errorbar(aes(ymax = up, ymin  = mu + 0, group = as.factor(delta)),
                position = position_dodge(1), width = 0, size = 1) +
  geom_bar(stat = "identity", position = position_dodge(1)) +
  geom_errorbar(aes(ymax = mu, ymin  = low),
                position = position_dodge(1),
                width = 0,
                size = 1,
                color = "white") +
  theme_bw() +
  facet_grid(measure ~ groups) +
  scale_fill_manual(name = "Method", values = c( "#009E73", "#0072B2", "#CC79A7", "#999999"),
                    breaks = c("10", "20", "30", "40", "100"),
                    labels = c(expression(~delta~" = 10"), 
                               expression(~delta~" = 20"), 
                               expression(~delta~" = 30"),   
                               expression(~delta~" = 40"),
                               " MLE")) +
  theme_bw(base_family = "Times", base_size = 13) +
  theme(legend.position = "note", strip.background = element_rect(fill = "grey93"),
        panel.grid.minor.y = element_blank(),
        legend.background = element_rect(color = "black"),
        panel.grid = element_line(color = "grey93")) +
  ylab("Score") +
  xlab("Sample Size")

# save(plot_3B, file = "plot_3B.Rdata")

```


Simulation 4: Plot 3C
```{r}
plot_3C <- res_df_4_summ %>%
  filter(method != "BF_alt") %>%
  filter(method != "mle") %>%
  ggplot(aes(x = as.factor(n), 
             y = mu, 
             fill = as.factor(delta))) +
  geom_errorbar(aes(ymax = up, 
                    ymin  = mu), 
                position = position_dodge(1), 
                width = 0, 
                size = 1) +
  geom_bar(stat = "identity", 
           position = position_dodge(1)) +
  geom_errorbar(aes(ymax = mu, 
                    ymin  = low),
                position = position_dodge(1),
                width = 0,
                size = 1,
                color = "white") +
  theme_bw() +
  facet_grid(measure~ groups) +
  scale_fill_manual(name = "Method", values = c( "#009E73", "#0072B2", 
                                                 "#CC79A7", "#999999")) +
  theme_bw(base_family = "Times", 
           base_size = 13) +
  theme(legend.position = "none", 
        strip.background = element_rect(fill = "grey93"),
        panel.grid.minor.y = element_blank(),
        legend.background = element_rect(color = "black"),
        panel.grid = element_line(color = "grey93")) +
  ylab("Score") +
  xlab("Sample Size")

# save(plot_3C, file = "plot_3C.Rdata")
# plot_3C
```



Application: Plot 4 Aand B
```{r, eval=FALSE}
pcors_g1 <- corpcor::cor2pcor(BGGM::ptsd_cor1)
pcors_g1_full <- ifelse(abs(pcors_g1) < 0.05, 0, pcors_g1)


pcors_g2 <- corpcor::cor2pcor(BGGM::ptsd_cor2)
pcors_g2_full <- ifelse(abs(pcors_g2) < 0.05, 0, pcors_g2)


pcors_g3 <- corpcor::cor2pcor(BGGM::ptsd_cor3)
pcors_g3_full <- ifelse(abs(pcors_g3) < 0.05, 0, pcors_g3)

pcors_g4 <- corpcor::cor2pcor(BGGM::ptsd_cor4)
pcors_g4_full <- ifelse(abs(pcors_g4) < 0.05, 0, pcors_g4)

pcors_g1[1:12, 1:16] <- 0
pcors_g1[14:16, 1:16] <- 0
pcors_g1[13, 13] <- 0


pcors_g2[1:12, 1:16] <- 0
pcors_g2[14:16, 1:16] <- 0
pcors_g2[13, 13] <- 0


pcors_g3[1:12, 1:16] <- 0
pcors_g3[14:16, 1:16] <- 0
pcors_g3[13, 13] <- 0

pcors_g4[1:12, 1:16] <- 0
pcors_g4[14:16, 1:16] <- 0
pcors_g4[13, 13] <- 0

pdf(file = "plot_app_ppc.pdf",  
    width = 7.5, 
    height = 3.5)

par(mfrow=c(2,4))

qgraph(pcors_g1_full, 
       label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73")

qgraph(pcors_g2_full, 
       label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73")

qgraph(pcors_g3_full, 
       label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73")

qgraph(pcors_g4_full,  label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73")


qgraph(pcors_g1, layout = "circle", 
       label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73")
qgraph(pcors_g2, layout = "circle", 
       label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73")
qgraph(pcors_g3, layout = "circle", 
       label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73")

qgraph(pcors_g4, layout = "circle", 
       label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73")
dev.off()

```


# Function for heatmaps
```{r}
GGM_compare_bf_plot <- function(X, cutoff){
  
  melt_01 <- reshape::melt(X$BF_01)
  melt_10 <- reshape::melt(X$BF_10)

  melt_01 <- subset(melt_01, value > cutoff)
  melt_01$X1 <- as.factor(melt_01$X1)

  max_01 <- log(max(melt_01$value))
  
  melt_10 <- subset(melt_10, value > cutoff)
  melt_10$X1 <- as.factor(melt_10$X1)
  max_10 <- log(max(melt_10$value))

  plt_null <- ggplot(melt_01, aes(x = as.factor(X2),
                                  y = as.factor(X1),
                                  fill = log(value))) +
    geom_tile() +
    scale_fill_gradientn(colours = c("white", "yellow", "red"),
                         values = c(0, .1, 1),
                         limits = c(log(cutoff), max_01),
                         labels = round(c(log(cutoff),    max_01)),
                         breaks =  c(log(cutoff),  max_01),
                         name = "BF 01") +

    xlab("Null Hypothesis Matrix") + ylab(" ") +
    ylim(rev(levels(melt_01$X1)))+
    theme_bw(base_size = 12) +
    theme(panel.grid = element_blank())  +
    theme(panel.grid = element_blank(),
          legend.title=element_text(size=9),
          legend.text=element_text(size=9))
  
  plt_alt <- ggplot(melt_10, aes(x = as.factor(X2),
                                 y = as.factor(X1),
                                 fill = round(log(value)))) +
    geom_tile() +
    scale_fill_gradientn(colours = c("white", "lightblue", "purple"),
                         values = c(0, .1, 1), limits = round(c(log(cutoff), max_10)),
                         labels = round(c(log(cutoff),   max_10)),
                         breaks =  round(c(log(cutoff),  max_10)),
                         name = "BF 10") +
    xlab("Alternative Hypothesis Matrix") + ylab(" ") +
    ylim(rev(levels(melt_10$X1)))+
    theme_bw(base_size = 12) +
    theme(panel.grid = element_blank(),
          legend.title=element_text(size=9),
          legend.text=element_text(size=9))

  list(plt_null = plt_null, plt_alt = plt_alt)
}
```

# Application plot 5
```{r}
Y_g1 <- MASS::mvrnorm(n = 526, 
                      mu = rep(0, 16), 
                      Sigma = BGGM::ptsd_cor1, 
                      empirical = T)

Y_g2 <- MASS::mvrnorm(n = 365, 
                      mu = rep(0, 16), 
                      Sigma = BGGM::ptsd_cor2, 
                      empirical = T)

Y_g3 <- MASS::mvrnorm(n = 926, 
                      mu = rep(0, 16), 
                      Sigma = BGGM::ptsd_cor3, 
                      empirical = T)

Y_g4 <- MASS::mvrnorm(n = 956, 
                      mu = rep(0, 16), 
                      Sigma = BGGM::ptsd_cor4, 
                      empirical = T)

fit <- ggm_compare_bf(Y_g1, Y_g2, 
                      Y_g3, Y_g4, 
                      prior_sd = 0.22, 
                      iter = 50000, 
                      cores = 4)

# select (BF = 3)
fit_sel <- select(fit, BF_cut = 3)

# plots
plts <- GGM_compare_bf_plot(fit_sel, cutoff = 3)

# null plot
plt_null <- plts$plt_null + 
  theme_bw(base_family = "Times", 
           base_size = 11) + 
  theme(panel.grid.major = element_blank(), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "top", 
        legend.direction = "horizontal", 
        legend.text = element_text(size = 8)) +
  xlab("Null Matrix") 

# alt plot
plt_alt <- plts$plt_alt + 
  theme_bw(base_family = "Times", base_size = 11) + 
  theme(panel.grid.major = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "top", 
        legend.direction = "horizontal", 
        legend.text = element_text(size = 8)) +
  xlab("Alternative Matrix") 

plot_5 <- plot_grid("", plt_null, "" , 
                    plt_alt, "", nrow = 1, 
                    rel_widths = c(.05,1,0.25,1,0.05))

# ggsave(plot_5, 
#        filename = "plot_5ms.pdf", 
#        width = 7.5, 
#        height = 3.75)
```

# Appendix: Network plot
```{r}
# base line
pcor4 <- corpcor::cor2pcor(as.matrix(BGGM::ptsd_cor4))
baseline <- ifelse(abs(pcor4) < 0.05, 0, pcor4) 

cut <- ifelse(abs(baseline) < 0.075, 0, baseline)

reduce <- baseline
reduce[1,3] <-  baseline[1,3] *.75 
reduce[3,1] <- reduce[1,3]

cut_n_reduce <- ifelse(abs(reduce) < 0.075, 0, reduce)

pdf(file = "plot_appendix.pdf",  
    width = 7.5, 
    height = 2.5)

par(mfrow=c(1,4))
qgraph(baseline, label.cex = 2,
        negCol = "#D55E00", 
       posCol = "#009E73", 
       title = "Baseline")

qgraph(cut, label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73", 
       title = "Cut")

qgraph(reduce, label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73", 
       title = "Reduce")

qgraph(cut_n_reduce, label.cex = 2,
       negCol = "#D55E00", 
       posCol = "#009E73", 
       title = "Both")
dev.off()
```

# Plot 1
```{r}
load("plot_1A.Rdata")
load("plot_1B.Rdata")
load("plot_1C.Rdata")

# top
top <- plot_grid(plot_1A, "", plot_1C, 
                 nrow = 1, rel_widths = c(1,0.2,1))

bottom <- plot_grid("", plot_1B, "", nrow = 1, 
                    rel_widths = c(0.05, 1, 0.05))
# plot 1
plot_1 <- plot_grid(top, bottom, nrow = 2, 
                    rel_heights = c(.6, 1))

# save
ggsave(plot_1, 
       filename = "plot_1ms.pdf", 
       width = 8, 
       height = 7.5)
```


Plot 3
```{r}
load("plot_3A.Rdata")
load("plot_3B.Rdata")
load("plot_3C.Rdata")

plot_3 <- plot_grid("", leg, "", plot_3A, 
                    plot_3B, plot_3C, 
                    nrow = 6, 
                    rel_heights = c(0.075, .1, 
                                    0.05,  1, 1, 1))

ggsave(plot_3, filename = "plot_3ms.pdf", 
       width = 8.5, height = 9.5)
```
